Investigating the Effect of Dataset Representivity for Image Colourisation

### 2019-10-09 Paper/paper.tex
Added final loss values

In order to determine the percentage of local data in the training dataset required to mitigate the effect of bias in machine learning models, multiple versions of the dataset are required, with each one consisting of a total of 40000 images and being constructed with a different percentage of South African images from 0\% to 40\% inclusive, increasing in graduations of 10\%. In addition to this training dataset, a validation dataset (of 1000 images in total) is also prepared with the same corresponding percentage inclusion of South African images.

@@

A Python script was used to assimilate the International and South African images into the required ratios (of 0\% to 40\% South African image inclusion) by randomly sampling $x$\% of images from the South African training split and $x$\% of images from the South African validation/testing split. The same number of images ($x$\%) was removed from the foreign dataset meaning that for each dataset, it contains $x$\% local data and ($100 - x$)\% foreign data where $x\in\{0, 10, 20, 30, 40\}$

@@

Due to the fact that images collected from Flickr were substantially larger in size than those of the European set, it took longer to train models with a high inclusion rate to the above mentioned epoch. For this reason, we chose to limit our inclusion of South African data to 40\%. Future experiments could show that an inclusion rate higher than 40\% is optimal but for the purpose of this experiment, it will suffice.

@@

\begin{table}[h]
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline 
Local inclusion \% & 10\% & 20\% & 30\% & 40\% \\ 
\hline 
Loss $\times 10^{-3}$& 2.638&2.638&2.638&2.638\\ 
\hline 
\end{tabular} 
\end{table}

>>>>

In order to determine the percentage of local data in the training dataset required to mitigate the effect of bias in machine learning models, multiple versions of the dataset are required, with each one consisting of a total of 40000 images and being constructed with a different percentage of South African images from 0\% to 30\% inclusive, increasing in graduations of 10\%. In addition to this training dataset, a validation dataset (of 1000 images in total) is also prepared with the same corresponding percentage inclusion of South African images.

@@

A Python script was used to assimilate the International and South African images into the required ratios (of 0\% to 30\% South African image inclusion) by randomly sampling $x$\% of images from the South African training split and $x$\% of images from the South African validation/testing split. The same number of images ($x$\%) was removed from the foreign dataset meaning that for each dataset, it contains $x$\% local data and ($100 - x$)\% foreign data where $x\in\{0, 10, 20, 30, 40\}$

@@

Due to the fact that images collected from Flickr were substantially larger in size than those of the European set, it took longer to train models with a high inclusion rate to the above mentioned epoch. For this reason, we chose to limit our inclusion of South African data to 30\%. Future experiments could show that an inclusion rate higher than 30\% is optimal but for the purpose of this experiment, it will suffice.

@@

\begin{table}[h]
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline 
Local inclusion \% & 0\% & 10\% & 20\% & 30\%  \\ 
\hline 
Loss $\times 10^{-3}$& 2.727 & 2.696 & 2.660 & 2.638\\ 
\hline 
\end{tabular} 
\end{table}
